### 2014-03-01 src/paper.Rnw
update

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
@
<<chunk-hook, echo=2>>=
<<setup>>
@
\end{comment}

@@

% 10 pages for the main text + 1 for references.
\section{Introduction}
<<>>=
load('data/opdist.rda')
@
% 1. Describe the problem
% 2. State your contributions

@@

r.all <- cbind(projects = rownames(r.pit.all), stack(r.pit.all))
r.all$ind <- clean(r.all$ind)
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Randoop'))
r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
@
\caption{Relative fertility of mutation operators}
\label{fig:mfert}

@@

\begin{figure*}[t]
% <<plots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% plot(sdl_f, main='SDL ~ ALL',pch='*')
% abline(sdl_all, col='red')
% plot(rnd_f, main='RND ~ ALL',pch='*')
% abline(rnd_all, col='blue')
% abline(sdl_all, col='red', lty=2)
% @
\caption{Plots}
\label{fig:caddrm}
\end{figure*}

\begin{figure*}[t]
% <<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% hist(log(10,m$sdl.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
% hist(log(10,m$sdl.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
% 
% hist(log(10,m$lrnd.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
% hist(log(10,m$lrnd.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
% 
% hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
% hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
% @
\caption{Plots of total mutation number, and those killed.}
\label{fig:caddrm}
\end{figure*}

>>>>

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
@
\end{comment}

@@

% 10 pages for the main text + 1 for references.
\section{Introduction}
<<>>=
data(o.pit.all)
data(o.pit.det)
data(r.pit.all)
data(r.pit.det)
@
% 1. Describe the problem
% 2. State your contributions

@@

r.all <- cbind(projects = rownames(r.pit.all), stack(r.pit.all))
r.all$ind <- clean(r.all$ind)
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='*',main='Randoop'))
r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c('darkgray'), add=T,pch='+'))
@
\caption{Relative fertility of mutation operators. The gray boxes represent detected mutants, while black represents total mutants.}
\label{fig:mfert}

@@
